Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Abstracts are hard.

% Draft 6
\textit{Nell} is a tablet-friendly\footnote{Nell's primary platform is the
XO-3, an affordable solar-powered tablet for kids in the developing world.}
education platform with a novel modular narrative system designed to engage
children in their own personal pursuit of literacy. Nell extends the design of
the \textit{Sugar Learning Platform}\footnote{\url{http://sugarlabs.org}} to
better support \textit{narrative} and \textit{personalization} and to better
accommodate \textit{growth}, \textit{authoring}, and \textit{direct
interaction}.
\end{abstract}

>>>>

%% % Draft 6
%% \textit{Nell} is a tablet-friendly\footnote{Nell's primary platform is the
%% XO-3, an affordable solar-powered tablet for kids in the developing world.}
%% education platform with a novel modular narrative system designed to engage
%% children in their own personal pursuit of literacy. Nell extends the design of
%% the \textit{Sugar Learning Platform}\footnote{\url{http://sugarlabs.org}} to
%% better support \textit{narrative} and \textit{personalization} and to better
%% accommodate \textit{growth}, \textit{authoring}, and \textit{direct
%% interaction}.

% Draft 7
% "education platform" -> "literacy platform"?
\textsc{Nell} is a tablet-oriented education platform for children in
the developing world.  A novel modular narrative system guides
learning, even for children far from educational infrastructure, and
provides personalized instruction which grows with the child.
Nell's design builds on experience with the Sugar Learning
Platform~\cite{sugar}, used by over a million children around the
world.

\end{abstract}
